Avancement du stage

### 2025-05-22 presentation.qmd
MAJ pipelines; MAJ carte retour

from app.utils.data_utils import (
    match_and_compare,
    add_metadata,
    dont_show_extreme,
    standardize_year,
    filter_nan
)
from app.utils.stats_utils import generate_metrics
from app.pipelines.import_quarto import (
    pipeline_data_quarto, pipeline_data_gev_quarto,
    pipeline_map_quarto,
    pipeline_map_legend_scatter,
    pipeline_title, pipeline_show_html,
    pipeline_quarto_gev_half_france
)

>>>>

from app.utils.data_utils import (
    match_and_compare,
    add_metadata,
    dont_show_extreme,
    standardize_year,
    filter_nan
)

from app.utils.stats_utils import generate_metrics

from app.pipelines.import_quarto import (
    pipeline_data_quarto, pipeline_data_gev_quarto,
    pipeline_map_quarto,
    pipeline_map_legend_scatter,
    pipeline_title, pipeline_show_html,
    pipeline_quarto_gev_half_france
)
